02_DESeq_hyp

### 2019-04-05 analysis/02_DESeq2_hyp.Rmd
now with for loop and wide DEGs

```{r}
library(tidyverse)
library(DESeq2)
library(cowplot)
library(RColorBrewer)
library(pheatmap)

@@

```{r resloop}
#create list of groups
a <- levels(colData$treatment)
a

# create list of groups, with control last
b <- a[2:9]
b[9] <- a[1]
b

for (i in a){
  for (j in b){
    print(paste(i,j))
    if (i != j) {
    numDEGs(i,j)
  }
  }
}
```

>>>>

```{r setup}
library(tidyverse)
library(DESeq2)
library(cowplot)
library(RColorBrewer)
library(pheatmap)
library(kableExtra)

@@

```{r resloop}
#create list of groups
a <- levels(colData$treatment)
b <- levels(colData$treatment)

# slim for testing
a <- c("n9", "bldg" , "lay" )
b <- c("n9", "bldg" , "lay" )

# comapre all contrasts, save to datafrmes
dat=data.frame()
for (i in a){
  for (j in b){
    if (i != j) {
      k <- paste(i,j, sep = "") #assigns usique rownames
      dat[k,1]<-i               
      dat[k,2]<-j
      dat[k,3]<- numDEGs(i,j) #caluculates number of DEGs
    }
  }
}

head(dat)
```

```{r restable}
# widen data to create table of degs
rownames(dat) <- NULL #remove row names
data_wide <- spread(dat, V2, V3)
data_wide
kable(data_wide) # pretty printing
```
